### 2013-12-01 index.Rmd
a quick table edit

-------------------
html-ouput                                          source code
------------                                        --------------
[loading, cleaning and summarizing](loadClean.html) [source](loadClean.Rmd)
-------------------

@@

-------------------
html-ouput                                        source code
------------                                      --------------
[Descriptive analysis](descriptive_analysis.html) [source](descriptive_analysis.Rmd)

[Spatial visualization](mapPlots.html)            [source]((mapPlots.Rmd))

[Graphics in the paper](finalPlots.html)          [source](finalPlots.Rmd)
-------------------

@@

-------------------
html-ouput                                                source code
------------                                              --------------
[Regression analysis](regressionModelling.html)           [source](regressionModelling.Rmd)

-------------------

@@

-------------------
pdf-output                                                source code
------------                                              --------------
[Article draft in .pdf](article2013.pdf)                  [source](article2013.Rmd)
-------------------

>>>>

| html-ouput | source code |
| ------------ | -------------- |
| [loading, cleaning and summarizing](loadClean.html) | [source](loadClean.Rmd) |

@@

| html-ouput | source code |
| ------------ | -------------- |
| [Descriptive analysis](descriptive_analysis.html) | [source](descriptive_analysis.Rmd) |
| [Spatial visualization](mapPlots.html) | [source](mapPlots.Rmd) |
| [Graphics in the paper](finalPlots.html) | [source](finalPlots.Rmd) |

@@

| html-ouput | source code |
| ------------ | -------------- |
| [Regression analysis](regressionModelling.html) | [source](regressionModelling.Rmd) |

@@

| pdf-ouput | source code |
| ------------ | -------------- |
| [Article draft in .pdf](article2013.pdf) | [source](article2013.Rmd) |
